Robust Adaptation to Multi-Scale Climate Variability

### 2019-04-08 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
Final version with manu suggestion

% Key Points
\begin{keypoints}
  \item \add{Climate risk varies over the planned lifespan of a climate risk mitigation instrument}
  \item \add{We carry out stylized computational experiments to assess the bias and variance of projected future risk estimated from limited data sets}
  \item \add{Lack of data limits the identifiability of climate signals, favoring prediction of short-term risks which require less extrapolation}
\end{keypoints}

@@

This need has motivated a multitude of approaches for estimating the probability distribution of future climate risk, and for choosing between different risk mitigation instruments based on these estimates \citep[see, e.g.\@\xspace,][]{Merz:2014gf}.
\add{A typical goal is to create systems which are robust in the sense that they perform well over a wide range of plausible futures} \citep{lempert:2007,Borgomeo:2018hk} \add{and which fail along non-catastrophic modes} \citep{brown:2010}.
Although climate risk has traditionally been managed with centrally planned structural instruments (e.g.\@\xspace, a levee), the high price \citep{Papakonstantinou:2016ve}, environmental costs \citep{dugan:2010}, and vulnerability to biased climate projections \citep{lempert:2007} have recently \remove{slowed their implementation}\add{dampened enthusiasm}.
\remove{Instead}\add{Rather}, actors such as New York City have turned to a combination of structural\add{ (e.g.\@\xspace, stormwater barrier)}, operational\add{ (e.g.\@\xspace, improved evacuation routes)}, and financial\add{ (e.g.\@\xspace, index insurance)} instruments for reducing vulnerability and increasing resilience to climate extremes \citep{CityofNewYork:2013uh}.
These instruments are not typically implemented in isolation or statically.
Instead, investment decisions made at each point in time affect the viability, costs, and benefits of future decisions, causing the system to trace a ``pathway'' through time \citep{Walker:2013gi,Haasnoot:2013im,Haasnoot:2015dh}.

@@

Typical climate risk management policies do not use a single risk mitigation instrument, but rather build a portfolio of several instruments.
Each has its own operational period, which may or may not match the planning horizon of the portfolio as a whole.
This means that even if the portfolio has a long planning period, i.e.\@\xspace if long-term plans are a priority, this goal may be best accomplished through a series of flexible and adaptive instruments with short individual planning periods.
\add{For example, the action that New York City can take today which best protects against uncertain hurricane risks over the 21st century could potentially be to purchase insurance and defer more permanent allocation of capital until some uncertainties are resolved.}
The costs and benefits of each individual instrument will be assessed over its individual, finite planning period, but decisions about the portfolio structure are evaluated over the longer planning horizon.

@@

External forcing from structured climate signals \citep[``teleconnections'';][]{Angstrom:1935ej} and catchment dynamics are both useful in explaining the \gls{lfv} observed in natural hydroclimate time series.
We illustrate such \gls{lfv} in \cref{fig:observed-lfv}, which shows a \SI{500}{year} drought reconstruction from the \gls{lbda} \citep{Cook:2010bz}, a \SI{100}{year} record of annual maximum streamflowflow on the American River at Folsom, and the global wavelet power spectrum for both \citep{Torrence:1998jp,Roesch:wlBQQoIs}.
Peaks for the American River time series are apparent at approximately 2 and 15 years and in the \gls{lbda} time series at approximately 8, 20, and 64 years.
This is illustrated by the blue line in \remove{the top left panel of} \cref{fig:observed-lfv}\add{(b)}, which shows a \SI{20}{year} moving average of the \gls{lbda} time series.
A detailed analysis of these time series is beyond the scope of this paper, but we note that the high amplitude and long time periods of the quasi-periodic oscillations they exhibit are consistent with analyses of \gls{lfv} in other hydroclimate systems \citep{Kiem:2002kq,Swierczynski:2012km,Woollings:2014kd,Hodgkins:2017hw}.
The key implication is that the observations, \citep{Jain:2001hz}, trends \citep{bhattacharya:1983}, and frequencies \citep{newman:2016} observed in the past are often poor predictors of future behavior.

@@

Both estimation bias and estimation uncertainty affect the utility of a climate risk projection, as illustrated in \cref{fig:conceptual-bias-variance}.
An instrument \add{whose design was based on projections with} \remove{designed based on} overestimated variance \remove{and}\add{or} positive bias will be over-designed, either causing the risk manager to avoid the investment, given its higher cost, or will lead to unnecessary diversion of funds from other instruments.
Similarly, an instrument designed based on underestimated variance or negative bias may be under-designed, and thus fail to protect the \remove{user}\add{public}.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Bias-Variance-Sketch.pdf}
  \caption{
    Consequences of model bias or incorrect model representation of uncertainty.
    If an estimate has a positive bias and overestimates uncertainty, the instrument may be too expensive.
    If an estimate has negative bias and underestimates uncertainty, it will be likely to fail.
  }\label{fig:conceptual-bias-variance}
\end{figure}

@@

\bibliography{library}

>>>>

% Key Points
\begin{keypoints}
  \item \add{Quasi-periodic and secular climate signals with different identifiability and predictability control uncertainty and risk into the future}
  \item \add{Adaptation strategies need to consider how the bias and variance in these risk predictions influences choices and decisions pathways}
  \item \add{Stylized experiments reveal how bias and variance of climate risk estimates over a finite planning periodinfluence risk mitigation}
\end{keypoints}

@@

This need has motivated a multitude of approaches for estimating the probability distribution of future climate risk, and for choosing between different risk mitigation instruments based on these estimates \citep[see, e.g.\@\xspace,][]{Merz:2014gf}.
\add{A typical goal is to create systems which are robust in the sense that they perform well over a wide range of plausible futures} \citep{lempert:2007,Borgomeo:2018hk} \add{and which fail along non-catastrophic modes} \citep{brown:2010}.
Although climate risk has traditionally been managed with centrally planned structural instruments (e.g.\@\xspace, a levee), the high price \citep{Papakonstantinou:2016ve}, environmental costs \citep{dugan:2010}, and vulnerability to biased climate projections \citep{lempert:2007} have recently \remove{slowed their implementation}\add{dampened enthusiasm}.
\remove{Instead}\add{Rather}, actors such as New York City have turned to a combination of structural\add{ (e.g.\@\xspace, stormwater barrier)}, operational\add{ (e.g.\@\xspace, improved evacuation routes)}, and financial\add{ (e.g.\@\xspace, a catastrophe bond)} instruments for reducing vulnerability and increasing resilience to climate extremes \citep{CityofNewYork:2013uh}.
These instruments are not typically implemented in isolation or statically.
Instead, investment decisions made at each point in time affect the viability, costs, and benefits of future decisions, causing the system to trace a ``pathway'' through time \citep{Walker:2013gi,Haasnoot:2013im,Haasnoot:2015dh}.

@@

Typical climate risk management policies do not use a single risk mitigation instrument, but rather build a portfolio of several instruments.
Each has its own operational period, which may or may not match the planning horizon of the portfolio as a whole.
This means that even if the portfolio has a long planning period, i.e.\@\xspace if long-term plans are a priority, this goal may be best accomplished through a series of flexible and adaptive instruments with short individual planning periods.
\add{For example, the optimal policy for New York City to manage uncertain hurricane risk in the 21st century might potentially be to keep areas devastated by hurricane Sandy zoned for low-impact development for the next 10 years.
This would reduce future risk over all climate scenarios while postponing major investments until large uncertainties as to the magnitude of future sea level rise are resolved.}
The costs and benefits of each individual instrument will be assessed over its individual, finite planning period, but decisions about the portfolio structure are evaluated over the longer planning horizon.

@@

External forcing from structured climate signals \citep[``teleconnections'';][]{Angstrom:1935ej} and catchment dynamics are both useful in explaining the \gls{lfv} observed in natural hydroclimate time series.
We illustrate such \gls{lfv} in \cref{fig:observed-lfv}, which shows a \SI{500}{year} drought reconstruction from the \gls{lbda} \citep{Cook:2010bz}, a \SI{100}{year} record of annual maximum streamflowflow on the American River at Folsom, and the global wavelet power spectrum for both \citep{Torrence:1998jp,Roesch:wlBQQoIs}.
Peaks for the American River time series are apparent at 2.3 and 15 years and in the \gls{lbda} time series at approximately 8, 20, and 64 years.
This is illustrated by the blue line in \remove{the top left panel of} \cref{fig:observed-lfv}\add{(b)}, which shows a \SI{20}{year} moving average of the \gls{lbda} time series.
A detailed analysis of these time series is beyond the scope of this paper, but we note that the high amplitude and long time periods of the quasi-periodic oscillations they exhibit are consistent with analyses of \gls{lfv} in other hydroclimate systems \citep{Kiem:2002kq,Swierczynski:2012km,Woollings:2014kd,Hodgkins:2017hw}.
The key implication is that the observations, \citep{Jain:2001hz}, trends \citep{bhattacharya:1983}, and frequencies \citep{newman:2016} observed in the past are often poor predictors of future behavior.

@@

Both estimation bias and estimation uncertainty affect the utility of a climate risk projection.
An instrument \add{whose design was based on projections with} \remove{designed based on} overestimated variance \remove{and}\add{or} positive bias will be over-designed, either causing the risk manager to avoid the investment, given its higher cost, or will lead to unnecessary diversion of funds from other instruments.
Similarly, an instrument designed based on underestimated variance or negative bias may be under-designed, and thus fail to protect the \remove{user}\add{public}.

@@

% -----------------------------------------------------------------------------
% REFERENCES
% -----------------------------------------------------------------------------

\begin{thebibliography}{}

  \bibitem [\protect \citeauthoryear {%
  Barnes%
  \ \BBA {} Screen%
  }{%
  Barnes%
  \ \BBA {} Screen%
  }{%
  {\protect \APACyear {2015}}%
  }]{%
  Barnes:2015gl}
  \APACinsertmetastar {%
  Barnes:2015gl}%
  \begin{APACrefauthors}%
  Barnes, E\BPBI A.%
  \BCBT {}\ \BBA {} Screen, J\BPBI A.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2015}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {The Impact of {{Arctic}} Warming on the Midlatitude
    Jet-Stream: {{Can}} It? {{Has}} It? {{Will}} It?} {The impact of {{Arctic}}
    warming on the midlatitude jet-stream: {{Can}} it? {{Has}} it? {{Will}}
    it?}{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Wiley Interdisciplinary Reviews-Climate
    Change}{6}{3}{277-286}.
  \newblock
  \begin{APACrefDOI} \doi{10.1002/wcc.337} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Beran%
  }{%
  Beran%
  }{%
  {\protect \APACyear {1994}}%
  }]{%
  beran:1994}
  \APACinsertmetastar {%
  beran:1994}%
  \begin{APACrefauthors}%
  Beran, J.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYear{1994}.
  \newblock
  \APACrefbtitle {Statistics for Long-Memory Processes} {Statistics for
    long-memory processes}.
  \newblock
  \APACaddressPublisher{New York}{{Chapman \& Hall}}.
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Betancourt%
  }{%
  Betancourt%
  }{%
  {\protect \APACyear {2017}}%
  }]{%
  Betancourt:2017vd}
  \APACinsertmetastar {%
  Betancourt:2017vd}%
  \begin{APACrefauthors}%
  Betancourt, M.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2017}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {A {{Conceptual Introduction}} to {{Hamiltonian Monte
    Carlo}}} {A {{Conceptual Introduction}} to {{Hamiltonian Monte
    Carlo}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{arXiv.org}{}{}{}.
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Bhattacharya%
  , Gupta%
  \BCBL {}\ \BBA {} Waymire%
  }{%
  Bhattacharya%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {1983}}%
  }]{%
  bhattacharya:1983}
  \APACinsertmetastar {%
  bhattacharya:1983}%
  \begin{APACrefauthors}%
  Bhattacharya, R\BPBI N.%
  , Gupta, V\BPBI K.%
  \BCBL {}\ \BBA {} Waymire, E.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{1983}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {The {{Hurst}} Effect under Trends} {The {{Hurst}} effect
    under trends}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Journal of Applied Probability}{20}{3}{649-662}.
  \newblock
  \begin{APACrefDOI} \doi{10.2307/3213900} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Blöschl%
  \ \BBA {} Montanari%
  }{%
  Blöschl%
  \ \BBA {} Montanari%
  }{%
  {\protect \APACyear {2010}}%
  }]{%
  bloschl:2010}
  \APACinsertmetastar {%
  bloschl:2010}%
  \begin{APACrefauthors}%
  Blöschl, G.%
  \BCBT {}\ \BBA {} Montanari, A.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2010}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Climate Change Impacts—Throwing the Dice?} {Climate
    change impacts—throwing the dice?}{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Hydrological Processes}{24}{3}{374-381}.
  \newblock
  \begin{APACrefDOI} \doi{10.1002/hyp.7574} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Borgomeo%
  , {Mortazavi-Naeini}%
  , Hall%
  \BCBL {}\ \BBA {} Guillod%
  }{%
  Borgomeo%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2018}}%
  }]{%
  Borgomeo:2018hk}
  \APACinsertmetastar {%
  Borgomeo:2018hk}%
  \begin{APACrefauthors}%
  Borgomeo, E.%
  , {Mortazavi-Naeini}, M.%
  , Hall, J\BPBI W.%
  \BCBL {}\ \BBA {} Guillod, B\BPBI P.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2018}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Risk, {{Robustness}} and {{Water Resources Planning
    Under Uncertainty}}} {Risk, {{Robustness}} and {{Water Resources Planning
    Under Uncertainty}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Earth's Future}{6}{3}{468-487}.
  \newblock
  \begin{APACrefDOI} \doi{10.1002/2017EF000730} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Bracken%
  , Rajagopalan%
  \BCBL {}\ \BBA {} Woodhouse%
  }{%
  Bracken%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2016}}%
  }]{%
  Bracken:2016ba}
  \APACinsertmetastar {%
  Bracken:2016ba}%
  \begin{APACrefauthors}%
  Bracken, C.%
  , Rajagopalan, B.%
  \BCBL {}\ \BBA {} Woodhouse, C.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2016}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {A {{Bayesian}} Hierarchical Nonhomogeneous Hidden
    {{Markov}} Model for Multisite Streamflow Reconstructions} {A {{Bayesian}}
    hierarchical nonhomogeneous hidden {{Markov}} model for multisite streamflow
    reconstructions}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Water Resources Research}{52}{10}{7837-7850}.
  \newblock
  \begin{APACrefDOI} \doi{10.1002/2016WR018887} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Brown%
  }{%
  Brown%
  }{%
  {\protect \APACyear {2010}}%
  }]{%
  brown:2010}
  \APACinsertmetastar {%
  brown:2010}%
  \begin{APACrefauthors}%
  Brown, C\BPBI M.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2010}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {The {{End}} of {{Reliability}}} {The {{End}} of
    {{Reliability}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Journal of Water Resources Planning and
    Management}{136}{2}{143-145}.
  \newblock
  \begin{APACrefDOI} \doi{10.1061/(ASCE)WR.1943-5452.65} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Bullmore%
  \ \protect \BOthers {.}}{%
  Bullmore%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2001}}%
  }]{%
  bullmore:2001}
  \APACinsertmetastar {%
  bullmore:2001}%
  \begin{APACrefauthors}%
  Bullmore, E.%
  , Long, C.%
  , Suckling, J.%
  , Fadili, J.%
  , Calvert, G.%
  , Zelaya, F.%
  \BDBL {}Brammer, M.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2001}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Colored Noise and Computational Inference in
    Neurophysiological ({{fMRI}}) Time Series Analysis: {{Resampling}} Methods in
    Time and Wavelet Domains} {Colored noise and computational inference in
    neurophysiological ({{fMRI}}) time series analysis: {{Resampling}} methods in
    time and wavelet domains}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Human Brain Mapping}{12}{2}{61-78}.
  \newblock
  \begin{APACrefDOI}
    \doi{10.1002/1097-0193(200102)12:2<61::AID-HBM1004>3.0.CO;2-W}
    \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Carpenter%
  \ \protect \BOthers {.}}{%
  Carpenter%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2017}}%
  }]{%
  Carpenter:2017ke}
  \APACinsertmetastar {%
  Carpenter:2017ke}%
  \begin{APACrefauthors}%
  Carpenter, B.%
  , Gelman, A.%
  , Hoffman, M\BPBI D.%
  , Lee, D.%
  , Goodrich, B.%
  , Betancourt, M.%
  \BDBL {}Riddell, A.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2017}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Stan: {{A Probabilistic Programming Language}}} {Stan:
    {{A Probabilistic Programming Language}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Journal Of Statistical Software}{76}{1}{1-29}.
  \newblock
  \begin{APACrefDOI} \doi{10.18637/jss.v076.i01} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Chamoli%
  , Ram~Bansal%
  \BCBL {}\ \BBA {} Dimri%
  }{%
  Chamoli%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2007}}%
  }]{%
  chamoli:2007}
  \APACinsertmetastar {%
  chamoli:2007}%
  \begin{APACrefauthors}%
  Chamoli, A.%
  , Ram~Bansal, A.%
  \BCBL {}\ \BBA {} Dimri, V\BPBI P.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2007}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Wavelet and Rescaled Range Approach for the {{Hurst}}
    Coefficient for Short and Long Time Series} {Wavelet and rescaled range
    approach for the {{Hurst}} coefficient for short and long time
    series}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Computers \& Geosciences}{33}{1}{83-93}.
  \newblock
  \begin{APACrefDOI} \doi{10.1016/j.cageo.2006.05.008} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  {City of New York}%
  }{%
  {City of New York}%
  }{%
  {\protect \APACyear {2013}}%
  }]{%
  CityofNewYork:2013uh}
  \APACinsertmetastar {%
  CityofNewYork:2013uh}%
  \begin{APACrefauthors}%
  {City of New York}.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2013}{}{}.
  \newblock
  \APACrefbtitle {A {{Stronger}}, {{More Resilient New York}}} {A {{Stronger}},
    {{More Resilient New York}}}\ \APACbVolEdTR{}{\BTR{}}.
  \newblock
  \APACaddressInstitution{New York}{}.
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Cook%
  \ \protect \BOthers {.}}{%
  Cook%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2010}}%
  }]{%
  Cook:2010bz}
  \APACinsertmetastar {%
  Cook:2010bz}%
  \begin{APACrefauthors}%
  Cook, E\BPBI R.%
  , Seager, R.%
  , Heim~Jr, R\BPBI R.%
  , Vose, R\BPBI S.%
  , Herweijer, C.%
  \BCBL {}\ \BBA {} Woodhouse, C.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2010}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Megadroughts in {{North America}}: Placing {{IPCC}}
    Projections of Hydroclimatic Change in a Long-Term Palaeoclimate Context}
    {Megadroughts in {{North America}}: Placing {{IPCC}} projections of
    hydroclimatic change in a long-term palaeoclimate context}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Journal of Quaternary Science}{25}{1}{48-61}.
  \newblock
  \begin{APACrefDOI} \doi{10.1002/jqs.1303} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Coumou%
  \ \BBA {} Rahmstorf%
  }{%
  Coumou%
  \ \BBA {} Rahmstorf%
  }{%
  {\protect \APACyear {2012}}%
  }]{%
  Coumou:2012bc}
  \APACinsertmetastar {%
  Coumou:2012bc}%
  \begin{APACrefauthors}%
  Coumou, D.%
  \BCBT {}\ \BBA {} Rahmstorf, S.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2012}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {A Decade of Weather Extremes} {A decade of weather
    extremes}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Nature Climate Change}{10}{7}{P100013-496}.
  \newblock
  \begin{APACrefDOI} \doi{10.1038/nclimate1452} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Delgado%
  , Merz%
  \BCBL {}\ \BBA {} Apel%
  }{%
  Delgado%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2014}}%
  }]{%
  Delgado:2014ey}
  \APACinsertmetastar {%
  Delgado:2014ey}%
  \begin{APACrefauthors}%
  Delgado, J\BPBI M.%
  , Merz, B.%
  \BCBL {}\ \BBA {} Apel, H.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2014}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Projecting Flood Hazard under Climate Change: An
    Alternative Approach to Model Chains} {Projecting flood hazard under climate
    change: An alternative approach to model chains}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Natural Hazards and Earth System
    Science}{14}{6}{1579-1589}.
  \newblock
  \begin{APACrefDOI} \doi{10.5194/nhess-14-1579-2014} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Di~Baldassarre%
  \ \protect \BOthers {.}}{%
  Di~Baldassarre%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2018}}%
  }]{%
  baldassarre:2018}
  \APACinsertmetastar {%
  baldassarre:2018}%
  \begin{APACrefauthors}%
  Di~Baldassarre, G.%
  , Kreibich, H.%
  , Vorogushyn, S.%
  , Aerts, J.%
  , {Arnbjerg-Nielsen}, K.%
  , Barendrecht, M.%
  \BDBL {}Ward, P\BPBI J.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2018}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Hess {{Opinions}}: {{An}} Interdisciplinary Research
    Agenda to Explore the Unintended Consequences of Structural Flood Protection}
    {Hess {{Opinions}}: {{An}} interdisciplinary research agenda to explore the
    unintended consequences of structural flood protection}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Hydrology and Earth System
    Sciences}{22}{11}{5629-5637}.
  \newblock
  \begin{APACrefDOI} \doi{https://doi.org/10.5194/hess-22-5629-2018}
    \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Dittes%
  , Špačková%
  , Schoppa%
  \BCBL {}\ \BBA {} Straub%
  }{%
  Dittes%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2017}}%
  }]{%
  Dittes:2017he}
  \APACinsertmetastar {%
  Dittes:2017he}%
  \begin{APACrefauthors}%
  Dittes, B.%
  , Špačková, O.%
  , Schoppa, L.%
  \BCBL {}\ \BBA {} Straub, D.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2017}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Climate Uncertainty in Flood Protection Planning}
    {Climate uncertainty in flood protection planning}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Hydrological and Earth System Science}{}{}{1-28}.
  \newblock
  \begin{APACrefDOI} \doi{10.5194/hess-2017-576} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Dugan%
  \ \protect \BOthers {.}}{%
  Dugan%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2010}}%
  }]{%
  dugan:2010}
  \APACinsertmetastar {%
  dugan:2010}%
  \begin{APACrefauthors}%
  Dugan, P\BPBI J.%
  , Barlow, C.%
  , Agostinho, A\BPBI A.%
  , Baran, E.%
  , Cada, G\BPBI F.%
  , Chen, D.%
  \BDBL {}Winemiller, K\BPBI O.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2010}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Fish {{Migration}}, {{Dams}}, and {{Loss}} of
    {{Ecosystem Services}} in the {{Mekong Basin}}} {Fish {{Migration}},
    {{Dams}}, and {{Loss}} of {{Ecosystem Services}} in the {{Mekong
    Basin}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{AMBIO}{39}{4}{344-348}.
  \newblock
  \begin{APACrefDOI} \doi{10.1007/s13280-010-0036-1} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Farnham%
  , {Doss-Gollin}%
  \BCBL {}\ \BBA {} Lall%
  }{%
  Farnham%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2018}}%
  }]{%
  Farnham:2018gs}
  \APACinsertmetastar {%
  Farnham:2018gs}%
  \begin{APACrefauthors}%
  Farnham, D\BPBI J.%
  , {Doss-Gollin}, J.%
  \BCBL {}\ \BBA {} Lall, U.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2018}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Regional {{Extreme Precipitation Events}}: {{Robust
    Inference From Credibly Simulated GCM Variables}}} {Regional {{Extreme
    Precipitation Events}}: {{Robust Inference From Credibly Simulated GCM
    Variables}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Water Resources Research}{}{}{}.
  \newblock
  \begin{APACrefDOI} \doi{10.1002/2017wr021318} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Feng%
  , Willemain%
  \BCBL {}\ \BBA {} Shang%
  }{%
  Feng%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2005}}%
  }]{%
  feng:2005}
  \APACinsertmetastar {%
  feng:2005}%
  \begin{APACrefauthors}%
  Feng, H.%
  , Willemain, T\BPBI R.%
  \BCBL {}\ \BBA {} Shang, N.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2005}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {Wavelet-{{Based Bootstrap}} for {{Time Series
    Analysis}}} {Wavelet-{{Based Bootstrap}} for {{Time Series
    Analysis}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Communications in Statistics - Simulation and
    Computation}{34}{2}{393-413}.
  \newblock
  \begin{APACrefDOI} \doi{10.1081/SAC-200055722} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  {GEI Consultants, Inc.}%
  }{%
  {GEI Consultants, Inc.}%
  }{%
  {\protect \APACyear {2017}}%
  }]{%
  GEI:gIaEZ-gS}
  \APACinsertmetastar {%
  GEI:gIaEZ-gS}%
  \begin{APACrefauthors}%
  {GEI Consultants, Inc.}%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2017}{}{}.
  \newblock
  \APACrefbtitle {Tulare {{Lake Storage}} and {{Floodwater Protection Feasibility
    Report}}} {Tulare {{Lake Storage}} and {{Floodwater Protection Feasibility
    Report}}}\ \APACbVolEdTR{}{\BTR{}}.
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Gelman%
  , Simpson%
  \BCBL {}\ \BBA {} Betancourt%
  }{%
  Gelman%
  \ \protect \BOthers {.}}{%
  {\protect \APACyear {2017}}%
  }]{%
  gelman:2017}
  \APACinsertmetastar {%
  gelman:2017}%
  \begin{APACrefauthors}%
  Gelman, A.%
  , Simpson, D.%
  \BCBL {}\ \BBA {} Betancourt, M.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{2017}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {The {{Prior Can Often Only Be Understood}} in the
    {{Context}} of the {{Likelihood}}} {The {{Prior Can Often Only Be
    Understood}} in the {{Context}} of the {{Likelihood}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Entropy}{19}{10}{555}.
  \newblock
  \begin{APACrefDOI} \doi{10.3390/e19100555} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}

  \bibitem [\protect \citeauthoryear {%
  Geweke%
  \ \BBA {} Porter‐Hudak%
  }{%
  Geweke%
  \ \BBA {} Porter‐Hudak%
  }{%
  {\protect \APACyear {1983}}%
  }]{%
  geweke:1983}
  \APACinsertmetastar {%
  geweke:1983}%
  \begin{APACrefauthors}%
  Geweke, J.%
  \BCBT {}\ \BBA {} Porter‐Hudak, S.%
  \end{APACrefauthors}%
  \unskip\
  \newblock
  \APACrefYearMonthDay{1983}{}{}.
  \newblock
  {\BBOQ}\APACrefatitle {The {{Estimation}} and {{Application}} of {{Long Memory
    Time Series Models}}} {The {{Estimation}} and {{Application}} of {{Long
    Memory Time Series Models}}}.{\BBCQ}
  \newblock
  \APACjournalVolNumPages{Journal of Time Series Analysis}{4}{4}{221-238}.
  \newblock
  \begin{APACrefDOI} \doi{10.1111/j.1467-9892.1983.tb00371.x} \end{APACrefDOI}
  \PrintBackRefs{\CurrentBib}
